# Videos

YouTube and other social media sharing sites have created an embarrassment of riches for prospective hams in terms of video content.
This page links to only a small fraction of the sites that one could explore.
If you find a video that tickles *your* fancy and might appeal to others, please send it our way.
Or, if you are GitHub savvy, just submit a pull request.

## What hams do {-}

```{r, echo=FALSE, fig.cap="[@Wolcott2023-uq](https://www.youtube.com/watch?v=wt5wZhC5crI)"}
knitr::include_url("https://www.youtube.com/embed/wt5wZhC5crI")
```

## Wave behavior {-}

```{r, echo=FALSE, fig.cap="[@Channel2012-ez](https://www.youtube.com/watch?v=DovunOxlY1k)"}
knitr::include_url("https://www.youtube.com/embed/DovunOxlY1k")
```

## Electronics {-}

### History of Ohms' Law

```{r, fig.cap="[@Kathy_Loves_Physics_History2021-cz]"}
knitr::include_url("https://www.youtube.com/embed/fk_BpXlfZ8U")
```

## Ham radio movie, *High Frequency* {-}

<iframe width="560" height="315" src="https://www.youtube.com/embed/cWQNyc-p-xI" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

## Getting licensed {-}

<iframe width="560" height="315" src="https://www.youtube.com/embed/ee_SkP-INsQ" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>


## Ham Radio Crash Course Technician class [@Course_undated-jl](http://www.youtube.com/playlist?list=PL1KAjn5rGhixvvb_jMZFWmbP97-t9Kyxk)  {-}

## References {-}
